Homicide Increases in the COVID-19 Era

### 2025-02-28 1_FirstDraft/Draft1.qmd
Organization

@@

>>>>

```{r, echo=FALSE}
ggplot(crime_la, aes(x = DateParsed, y = Vict.Sex, color = Vict.Sex)) +
  geom_jitter(alpha = 0.4, width = 0.2) +
  labs(title = "Crime Over Time by Gender",
       x = "Date",
       y = "Gender") +
  theme_minimal()

@@

crime_la$Hour <- as.numeric(format(crime_la$DateParsed, "%H"))

ggplot(crime_la, aes(x = Hour, fill = ..density..)) +
  geom_density(alpha = 0.5, color = "black") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Crime Density Per Hour",
       x = "Hour",
       y = "Density") +
  theme_minimal()

### 2025-02-28 2_SecondDraft/Draft2.qmd
Organization

ggplot(data = long_Cor, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(direction = -1) +
  theme(axis.title.x =  element_blank(),
        axis.title.y = element_blank()) +
  geom_text(aes(label = value), color = "black", size = 4) + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size=12)) + 
  ggtitle("Correlations Between the Number of Crimes and \n Different Law Enforcement and Socioeconomic Factors")
```

## geom_jitter
## geom_jitter

>>>>

ggplot(data = long_Cor, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(direction = -1) +
  theme(axis.title.x =  element_blank(),
        axis.title.y = element_blank()) +
  geom_text(aes(label = value), color = "black", size = 4) + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size=12)) + 
  ggtitle("Correlations Between the Number of Crimes and \n Different Law Enforcement and Socioeconomic Factors")
```
## geom_jitter
